\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-04-19 sections/methods.tex
Add: Section about NI statistical analyses

  \subsubsection*{NI step}
  % Write about precision and sensitivity equations used
  % L1 distance equations used

>>>>

  \subsubsection*{NI step}
  % Write about precision and sensitivity equations used
  In Figure~\ref{fig:figure6} we calculate the accuracy and robustness of the inferred association networks (using the various network inference algorithms and the consensus methods) against the original interaction used to create the taxonomic distribution.
  We use precision and sensitivity to calculate the accuracy of the predictions.
  Precision is given by, $\frac{TP}{TP + FP}$
  Sensitivity is given by, $\frac{TP}{FN + TP}$
  % L1 distance equations used
  In Figure~\ref{fig:figure7}B we use the L1 distance metric to measure to the distance between the network inferred using different tools at the same step of the workflow.
  The L1 distance between networks $x$ and $y$ is calculated using the following formula:
  $$ \frac{|A_{x}-A_{y}|}{2} $$, where $A$ is the adjacency matrix of the network.
